OpenMPIR

### 2017-09-06 paper.tex
Added lanl acks

\section*{Acknowledgment}
Sandia National Laboratories is a multimission laboratory managed and operated 
by National Technology and Engineering Solutions of Sandia, LLC., a wholly 
owned subsidiary of Honeywell International, Inc., for the U.S. Department of 
Energy’s National Nuclear Security Administration under contract DE-NA-0003525.

>>>>

\section*{Acknowledgments}
Sandia National Laboratories is a multimission laboratory managed and operated 
by National Technology and Engineering Solutions of Sandia, LLC., a wholly 
owned subsidiary of Honeywell International, Inc., for the U.S. Department of 
Energy’s National Nuclear Security Administration under contract DE-NA-0003525.

This work was supported by the Director, Office of Advanced Scientific
Computing Research, Office of Science, of the United States Department
of Energy, under the guidance of Dr. Sonia Sachs. Los Alamos National
Laboratory is operated by Los Alamos National Security LLC for the U.S.
Department of Energy under contract DE-AC52-06NA25396.

This research was supported by US National Science Foundation under CRII
ACI 1565338, CNS 1527076, and CNS 1217948. Los Alamos National
Laboratory is operated by Los Alamos National Security LLC for the US
Department of Energy under contract DE-AC52-06NA25396.

Work supported by the Advanced Simulation and Computing program of the
U.S. Department of Energy's NNSA\@.  Los Alamos National Laboratory is
managed and operated by Los Alamos National Security, LLC (LANS), under
contract number DE-AC52-06NA25396 for the Department of Energy’s
National Nuclear Security Administration (NNSA).
